Are We Reusing Outdated and License-violating Code \newline from Stack Overflow?

### 2017-01-29 cloneoverflow-latex/cloneoverflow.tex
Added Gabel and Su.
Updated the number of ok pairs

\begin{table}
	\centering
	\caption{The number of online clone pair condidates (mutually exclusive) before and after filtering.}
	\label{tab:online_clone_pairs}
	\small
%	\resizebox{\columnwidth}{!}{%
	\begin{tabular}{l|r|c|c|c|c|r}
		\hline
		\multirow{2}{*}{Set} & \multicolumn{1}{c|}{Before} & \multicolumn{4}{c|}{Filters*} & \multirow{2}{*}{Cand.} \\ \cline{3-6}
		& \multicolumn{1}{c|}{Filters} & \textit{L} & \textit{S} & \textit{R} & \textit{G} & \\
		\hline 
		\multirow{1}{*}{\textit{good}} & 2,261 & & & & & 2,261 \\
		\multirow{1}{*}{\textit{ok}} & 9,322 & & & & & 9,322 \\
		%\multirow{1}{*}{\textit{agreed clone pairs}}      & 29,099 \\
		\multirow{1}{*}{$S_D$} & 67,570 & \checkmark & & \checkmark & \checkmark & 17,801 \\
		\multirow{1}{*}{$N_D$} & 229,176 & & \checkmark & \checkmark & \checkmark & 168 \\ 
		%\multirow{1}{*}{\textit{disagreed clone pairs}}    & 1,039 \\
		\hline
		Total  & 296,746 & & & & & 28,832 \\ 
		\hline
		\multicolumn{7}{l}{\scriptsize{Filters*: \textit{L}=$Line \geq 10$, \textit{S}=$Sim \geq 80\%$,}} \\
		\multicolumn{7}{l}{\scriptsize{\textit{R}=regular expressions, and \textit{G}=\textit{good}/\textit{ok} pairs.}} \\
	\end{tabular} %
%}
\end{table}

@@

Even choosing only the default configurations, the number of clone pair candidates are still very large. We hence apply three filters: \textbf{clone size, regular expression, and similarity threshold}. For the clone size filter, we raise the minimum clone size to 10 line as larger clones tend to be more interesting while smaller ones tend to be false clones \cite{Saini2016}. The 10--line threshold is already the default configuration for NiCad, thus this filter affects Simian clone pairs only (Simian's default configurations consider a minimum of 6 lines).~The regular expression filter captures uninteresting boiler-plate clones of \verb|hashCode()| methods, getters and setters using regular expressions and removes them. The third filter, similarity threshold, applies only to NiCad clone pairs since Simian does not provide this similarity threshold configuration. %We increase the similarity threshold of NiCad clone pairs from 70\% to 80\%. %Using the filter along with regular expressions to capture boiler-plate code clones such as \verb|equals()| and \verb|hashcode()|, we can reduce the number of Simian clone candidates to a manageable amount of 795 clone pairs.

@@

The outdate online code clones can cause problems ranging from uncompilable code due to different API usage to bug propagation. An outdated code with a subtle change (e.g.~\Cref{fig:before-after}) may be copied and reused without awareness from developers. Stack Overflow has a voting mechanism that may mitigate this outdated code issue. Usually when developers reuse a code snippet from a Stack Overflow post and find that it does not work nor compatible with their environment. They can cast a down vote to that answer resulting in low votes for the answer (which might be outdated). However, if the answer is marked as accepted by the person who asks the question (which is our case), it is always ranked on the top and still attractive to naive developers who are ignorant.

>>>>

\begin{table}
	\centering
	\caption{The number of online clone pair condidates (mutually exclusive) before and after filtering.}
	\label{tab:online_clone_pairs}
	\small
%	\resizebox{\columnwidth}{!}{%
	\begin{tabular}{l|r|c|c|c|c|r}
		\hline
		\multirow{2}{*}{Set} & \multicolumn{1}{c|}{Before} & \multicolumn{4}{c|}{Filters*} & \multirow{2}{*}{Cand.} \\ \cline{3-6}
		& \multicolumn{1}{c|}{Filters} & \textit{L} & \textit{S} & \textit{R} & \textit{G} & \\
		\hline 
		\multirow{1}{*}{\textit{good}} & 2,261 & & & & & 2,261 \\
		\multirow{1}{*}{\textit{ok}} & 9,322 & & & & & 9,322 \\
		%\multirow{1}{*}{\textit{agreed clone pairs}}      & 29,099 \\
		\multirow{1}{*}{$S_D$} & 67,570 & \checkmark & & \checkmark & \checkmark & 17,801 \\
		\multirow{1}{*}{$N_D$} & 229,176 & & \checkmark & \checkmark & \checkmark & 168 \\ 
		%\multirow{1}{*}{\textit{disagreed clone pairs}}    & 1,039 \\
		\hline
		Total  & 296,746 & & & & & 28,832 \\ 
		\hline
		\multicolumn{7}{l}{\scriptsize{Filters*: \textit{L}=$Line \geq 10$, \textit{S}=$Sim \geq 85\%$,}} \\
		\multicolumn{7}{l}{\scriptsize{\textit{R}=regular expressions, and \textit{G}=\textit{good}/\textit{ok} pairs.}} \\
	\end{tabular} %
%}
\end{table}

@@

Even choosing only the default configurations, the number of clone pair candidates are still very large. We hence apply three filters: \textbf{clone size, regular expression, and similarity threshold}. For the clone size filter, we raise the minimum clone size to 10 line as larger clones tend to be more interesting while smaller ones tend to be false clones \cite{Saini2016}. Moreover, Gabel and Su show that unique code tend to be larger than seven lines \cite{Gabel2010}. The 10--line threshold is already the default configuration for NiCad, thus this filter affects Simian clone pairs only (Simian's default configurations consider a minimum of 6 lines).~The regular expression filter captures uninteresting boiler-plate clones of \verb|hashCode()| methods, getters and setters using regular expressions and removes them. The third filter, similarity threshold, applies only to NiCad clone pairs since Simian does not provide this similarity threshold configuration. %We increase the similarity threshold of NiCad clone pairs from 70\% to 80\%. %Using the filter along with regular expressions to capture boiler-plate code clones such as \verb|equals()| and \verb|hashcode()|, we can reduce the number of Simian clone candidates to a manageable amount of 795 clone pairs.

@@

The outdate online code clones can cause problems ranging from uncompilable code due to different API usage to bug propagation. An outdated code with a subtle change (e.g.~\Cref{fig:before-after}) may be copied and reused without awareness from developers. Although Stack Overflow has a voting mechanism that may mitigate this outdated code issue, the check mark symbol in front of the accepted answer is still attractive to naive developers who are ignorant.
%Usually when developers reuse a code snippet from a Stack Overflow post and find that it does not work nor compatible with their environment. They can cast a down vote to that answer resulting in low votes for the answer (which might be outdated). However, if the answer is marked as accepted by the person who asks the question, the check mark symbol attached to the answer is still attractive to naive developers who are ignorant.
